\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-17 grassposter/2014_EGU_G7_Landscape/poster.tex
2014_EGU_G7_Landscape: added TGRASS content
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59756 15284696-431f-4ddb-bdfa-cd5b030d7da7

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
% needed for authors:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{TGRASS: temporal framework}{
[Gebbert 2014]
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);

>>>>

\documentclass[landscape,a0,final]{a0poster}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{tikzposter} % here most of the things are defined
% change parameters only after this line You can also start a new column with an arbitrary 
% x-coordinate by specifying explicitly the coordinate of the new block node as follows:
% needed for authors:
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{wrapfig}
\usepackage{url}
\usepackage{alltt}
\usepackage{textcomp}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\blocknode{TGRASS: temporal framework}{
TGRASS [Gebbert 2014] provides support for large spatio-temporal data handling and analysis, and is fully integrated into GRASS GIS 7.
It introduces the concept of space-time dataset as a series of vector, raster, or 3D raster data with temporal metadata.
In the simple example below, we computed a series of vector data representing particles in a water flow simulation,
created a space-time dataset and registered the vectors to this dataset based on time stamps assigned during the vector creation.
The result can be then quickly visualized using GRASS GIS Animation Tool.

{\small
\begin{alltt}
r.sim.water -t elevation=elev\_lid792\_1m dx=dx dy=dy depth=depth outwalk=walker outiter=1

\textcolor{DarkGreen}{t.create} output=particles type=stvds temporaltype=relative semantictype=mean title="Particles"~desc="Particles"

\textcolor{DarkGreen}{t.register} input=particles maps=\textasciigrave g.mlist --q type=vect pattern=walker* separator=,\textasciigrave{} type=vect

g.gui.animation stvds=particles
\end{alltt}}

\begin{center}
\includegraphics[width=\textwidth]{images/particles}
\end{center}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\getcurrentrow{box}
\coordinate (funkcionalita) at (box.south west);
\coordinate (funkcionalitaeast) at (box.east);
\coordinate (screenshot) at (box.north west);
